%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
% Requires DejaVuSansMono and LinLibettine fonts
% Download Deja Vu here: http://dejavu-fonts.org/wiki/Download
% and lin libertine here: http://www.dafont.com/linux-libertine.font
% For libertine you need R, RB, RBI, and RI fonts
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letter]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
bookmarks, colorlinks, breaklinks=true,
	pdftitle={Ryan Schuetzler - Vita},
	pdfauthor={Ryan Schuetzler},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE Ryan M. Schuetzler, Ph.D.}\\[1cm]
Brigham Young University\\
Provo, UT \texttt{84602}
U.S.A.\\[.2cm]
% Phone: \texttt{(402) 554-3007}\\[.2cm]
email: \href{mailto:ryan.schuetzler@byu.edu}{ryan.schuetzler@byu.edu}\\

%%\hrule
\section*{Current Position}
\emph{Assistant Professor}\\
Department of Information Systems\\
Marriott School of Management\\
Brigham Young University


\section*{Research Interests}

In my research, I focus on how people respond to new technology, and how that technology can be built to interact with users most effectively.
My primary research focuses on human interaction with embodied conversational agents, robots, and chatbots, and the influence of those chat bots on users' feelings and behavior toward those systems. 
I am interested to learn how people adapt their behavior, either consciously or unconsciously, as they interact with these types of novel systems. 

%\hrule
\section*{Previous Appointments}
\noindent
\years{2015-2020}University of Nebraska at Omaha, Assistant Professor

%\hrule
\section*{Education}
\noindent
\years{2015}\textsc{Ph.D.} in Management Information Systems, University of Arizona\\
\years{2010}\textsc{MS} in Information Systems Management, Brigham Young University\\
\years{2010}\textsc{BS} in Information Systems, Brigham Young University

%\hrule
\section*{Grants, Honors \& Awards}
\noindent
\years{2019-2020}Principal Investigator, \emph{The Role of Expectations in Shaping Impressions of Artificial Intelligence}, 
University Committee on Research and Creative Activity, University of Nebraska at Omaha, \$5,000.\\

\years{2015--2018}Principal investigator, \emph{Dynamic Interviewing Agents},
Nebraska Research Initiative, \$200,000.\\

\years{2015}Co-investigator, \emph{Decision Support Capabilities for National
	Leadership}, National Strategic Research Institute, \$249,875.

\newpage
\section*{Publications \& Talks}

\textbf{*} Indicates student co-authors

\subsection*{Selected publications}
\noindent
\years{2022}Schuetzler, R., Giboney, J., \& Grimes, G. M. (2022). Design of a Chatbot Social Engineering Victim. \emph{Hawaii International Conference on System Sciences}. January 3--7.\\

\years{}Leavitt, C.\textbf{*}, Corbin, M.\textbf{*}, Keith, M., Schuetzler, R., Anderson, G., \& Kettles, D. (2022). A Chatbot Tutor Can Lessen the Gender Confidence Gap in Information Systems Learning. \emph{Hawaii International Conference on System Sciences}. January 3--7.\\

\years{2021}Grimes, G. M., Schuetzler, R. M., \& Giboney, J.S. (2021). Mental Models and Expectation Violations in Conversational AI Interactions.
\emph{Decision Support Systems, 144}. \doi{https://doi.org/10.1016/j.dss.2021.113515}\\

\years{}Schuetzler, R. M., Grimes, G. M., Giboney, J. S., \& Rosser, H. K.\textbf{*} (2021). Deciding Whether and How to Deploy Chatbots.
\emph{MIS Quarterly Executive, 20}(1), p. 4.\\

\years{2020} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2020). 
The Impact of Chatbot Conversational Skill on Engagement and Perceived Humanness. 
\emph{Journal of Management Information Systems, 37}(3), pp.\ 875-900. 
\doi{https://doi.org/10.1080/07421222.2020.1790204}\\

\years{} Pickard, M., Schuetzler, R. M., Valacich, J. S., \& Wood, D. A. (2020). 
Innovative Accounting Interviewing: A Comparison of Real and Virtual Accounting Interviewers. 
\emph{The Accounting Review, 95}(6), pp.\ 339--366.
\doi{https://doi.org/10.2308/tar-2017-0235}\\

\years{2019} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2019). 
The Effect of Conversational Agent Skill on User Behavior during Deception. 
\emph{Computers in Human Behavior, 97}, pp.\ 250--259. \doi{https://doi.org/10.1016/j.chb.2019.03.033}\\

\years{}Marquardson, J. \& Schuetzler, R. M. (2019). Teaching Tip: Learning by Teaching through Collaborative Tutorial Creation: Experience using GitHub and AsciiDoc. \emph{Journal of Information Systems Education, 30}(1), pp.\ 10--18.\\

\years{}Schuetzler, R. M., Morrison, B. B., \& Hayes, J. (2019). Digital Excellence: A Missing Link. \emph{Americas Conference on Information Systems}, Canc\'{u}n, Mexico, August 15--17.\\

\years{2018}Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Nunamaker, J. F. (2018).
The Influence of Conversational Agent Embodiment and Conversational Relevance on Socially Desirable Responding.
\emph{Decision Support Systems, 114}, pp.\ 94--102. \doi{https://doi.org/10.1016/j.dss.2018.08.011}


\subsection*{Invited Presentations and Panels}
\noindent
\years{2022}\emph{When Should a Chatbot Be Less Chatty}. Presentation at AMCIS Workshop on Artificial Intelligence and Human Interaction, Minneapolis, MN.\\

\years{2021}\emph{The Value of Tailoring and Small Talk}. Presentation at the Dagstuhl Seminar: Conversational Agent as Trustworthy Autonomous System (Trust-CA).\\


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
	{\scriptsize  Last updated: \today\- •\-
		% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
		Typeset in \href{http://nitens.org/taraborelli/cvtex}{
			%\fontspec{Times New Roman}
			\XeTeX }\\
		% ---- FILL IN THE FULL URL TO YOUR CV HERE
		% \href{http://nitens.org/taraborelli/cvtex}{http://nitens.org/taraborelli/cvtex}
	}
\end{center}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
