%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
% Requires DejaVuSansMono and LinLibettine fonts
% Download Deja Vu here: http://dejavu-fonts.org/wiki/Download
% and lin libertine here: http://www.dafont.com/linux-libertine.font
% For libertine you need R, RB, RBI, and RI fonts
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letter]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
bookmarks, colorlinks, breaklinks=true,
	pdftitle={Ryan Schuetzler - Vita},
	pdfauthor={Ryan Schuetzler},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE Ryan M. Schuetzler, Ph.D.}\\[1cm]
 Information Systems and Quantitative Analysis Department\\
U.S.A.\\[.2cm]
Phone: \texttt{(402) 554-3007}\\[.2cm]
email: \href{mailto:rschuetzler@unomaha.edu}{rschuetzler@unomaha.edu}\\

%%\hrule
\section*{Current Position}
\emph{Assistant Professor}\\
Information Systems and Quantitative Analysis Department\\
College of Information Science \& Technology\\
University of Nebraska at Omaha


\section*{Research Interests}

My research interests center around users' adaptation and use of novel communication technology. 
My primary research focuses on human interaction with embodied conversational agents and chat bots, and the influence of those chat bots on users' feelings and behavior toward those systems. 
I also study users' adaptation to intelligent systems designed to detect deception. 
I am interested to learn how people adapt their behavior, either consciously or unconsciously, as they interact with novel systems. 


%\hrule
\section*{Education}
\noindent
\years{2015}\textsc{Ph.D.} in Management Information Systems, University of Arizona\\
\years{2010}\textsc{MS} in Information Systems Management, Brigham Young University\\
\years{2010}\textsc{BS} in Information Systems, Brigham Young University


\section*{Most Recent Relevant Publications}

\subsection*{Journal articles}
\noindent
\years{2019}Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2019). The Effect of Conversational Agent Skill on User Behavior during Deception. \emph{Computers in Human Behavior, 97}, pp.\ 250--259.\\

\years{2018}Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Nunamaker, J. F. (2018).
The Influence of Conversational Agent Embodiment and Conversational Relevance on Socially Desirable Responding.
\emph{Decision Support Systems, 114}, pp.\ 94--102.\\

\years{2015} Twyman, N. T., Proudfoot, J. G., Schuetzler, R., Elkins,
A. C., \& Derrick, D. C. (2015). Robustness of multiple indicators in
controlled, automated deception detection interviews. \emph{Journal of
  Management Information Systems, 32}(4), pp.\ 215--245.\\

\subsection*{Conference proceedings}
\noindent

\years{2018}Pickard, M. D., Schuetzler, R. M., Valacich, J. S., \& Wood, D. (2018).
Next-Generation Accounting Interviewing: A Comparison of Human and Embodied Conversational Agents (ECAs) as Interviewers.
\emph{American Accounting Association Midyear Meeting}, Newport Beach, CA, January 18--20.\\

\years{} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2018).
An Investigation of Conversational Agent Relevance, Presence, and Engagement
\emph{Americas Conference on Information Systems}, New Orleans, LA, August 15--18.\\

\years{} Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Nunamaker, J.
F. (2018) The Influence of Conversational Agents on Socially Desirable
Responding. \emph{Hawaii International Conference on System Sciences}. Waikoloa Village, HI, January 3--6.\\

\years{2016}Schuetzler, R. M., Grimes, G. M., Elkins, A. C., Burgoon, J. K., \&
Valacich, J. S. (2016) Talking and typing: A comparison of vocalic and keystroke
dynamic features for deception detection. \emph{Hawaii International Conference
  on System Sciences}. Koloa, HI, January 5--8.\\

\years{2014}Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Buckman,
J. (2014) Facilitating natural conversational agent interactions: Lessons from a
deception experiment. \emph{International Conference on Information Systems}. Auckland, New Zealand, December 12-16.\\


\subsection*{Invited Presentations and Panels}
\noindent

\years{2016}\emph{Chatbot for Enhancing Voluntary Information Disclosure}. Webinar for the Center for Identification
Technology Research, an NSF Industry/University Collaborative Research Center.\\

\years{2015}\emph{Lie to Me: Chatterbot Style}. Webinar for the Center for Identification
Technology Research, an NSF Industry/University Collaborative Research Center.\\

\emph{A Mobile Interviewing Agent for Deception Detection}. Webinar for the
Center for Identification Technology Research, an NSF Industry/University Collaborative
Research Center.\\

\years{2012-2014}\emph{Deception and Automated Credibility Assessment}. Fort Huachuca
Military Intelligence Captain's Career course.


\section*{Technical and Other Skills}

\begin{itemize}
\itemsep0em
\item Programming languages: Python, R, Node.js
\item Web application development with Python and Django
\item TCP/IP networking (formerly CCNA certified)
\item SQL \& database management
\item Linux and Windows servers
\end{itemize}


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
% \href{http://nitens.org/taraborelli/cvtex}{http://nitens.org/taraborelli/cvtex}
}
\end{center}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
