%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
% Requires DejaVuSansMono and LinLibettine fonts
% Download Deja Vu here: http://dejavu-fonts.org/wiki/Download
% and lin libertine here: http://www.dafont.com/linux-libertine.font
% For libertine you need R, RB, RBI, and RI fonts
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, letter]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
bookmarks, colorlinks, breaklinks=true,
	pdftitle={Ryan Schuetzler - Vita},
	pdfauthor={Ryan Schuetzler},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE Ryan M. Schuetzler, Ph.D.}\\[1cm]
Department of Information Systems\\
Marriott School of Management\\
Brigham Young University\\
Provo, UT \texttt{84602}
U.S.A.\\[.2cm]
% Phone: \texttt{(402) 554-3007}\\[.2cm]
email: \href{mailto:ryan.schuetzler@byu.edu}{ryan.schuetzler@byu.edu}\\
\textsc{url}: \href{https://www.schuetzler.net}{https://www.schuetzler.net}\\

%%\hrule
\section*{Current Position}
\emph{Assistant Professor}\\
Department of Information Systems\\
Marriott School of Management\\
Brigham Young University


\section*{Research Interests}

My research centers on users' adaptation and use of novel communication technology. 
My primary research focuses on human interaction with embodied conversational agents and chat bots, and the influence of those chat bots on users' feelings and behavior toward those systems. 
I also study users' adaptation to intelligent systems designed to detect deception. 
I am interested to learn how people adapt their behavior, either consciously or unconsciously, as they interact with novel systems. 


%%\hrule
\section*{Areas of Specialization}
%! Fill this out
Conversational Agents $\bullet$ Human-Computer Interaction $\bullet$ Privacy $\bullet$ Deception

%\hrule
\section*{Previous Appointments}
\noindent
\years{2015-2020}University of Nebraska at Omaha, Assistant Professor\\
% \years{1908-1911}University of Bern\\
% \years{1911-1912}University of Zürich\\
% \years{1912-1914}Charles University of Prague\\
% \years{1914-1932}Prussian Academy of Sciences, Berlin\\
% \years{1920-1930}University of Leiden\\
% \years{1932-1955}Institute for Advanced Study, Princeton

%\hrule
\section*{Education}
\noindent
\years{2015}\textsc{Ph.D.} in Management Information Systems, University of Arizona\\
\years{2010}\textsc{MS} in Information Systems Management, Brigham Young University\\
\years{2010}\textsc{BS} in Information Systems, Brigham Young University

%\hrule
\section*{Grants, Honors \& Awards}
\noindent
\years{2019-2020}Principal Investigator, \emph{The Role of Expectations in Shaping Impressions of Artificial Intelligence}, 
University Committee on Research and Creative Activity, University of Nebraska at Omaha, \$5,000.\\

\years{2016-2019}Co-investigator, \emph{Optimizing EHR Usability for Cardiac Care},
Agency for Healthcare Research and Quality, \$571,835.\\

\years{2015--2018}Principal investigator, \emph{Dynamic Interviewing Agents},
Nebraska Research Initiative, \$200,000.\\

\years{2015}Co-investigator, \emph{Decision Support Capabilities for National
	Leadership}, National Strategic Research Institute, \$249,875.\\


\years{2011--2014} \$205,000 in research grants, Center for Identification
Technology Research\\

\years{2011} Science Foundation Arizona Graduate Research Fellow

\subsection*{Awards}

\years{2020} University of Nebraska at Omaha Alumni Outstanding Teaching Award\\

\years{} Outstanding officer award as President of the Midwest Chapter of the Association for Information Systems

\years{2018} Best paper for ``Next-Generation Accounting Interviewing: A Comparison of Human and Embodied Conversational Agents (ECAs) as Interviewers'' at American Accounting Association Midyear Meeting\\

\years{} Best paper for ``Learning by Teaching through Collaborative Tutorial Creation: Experience using GitHub and AsciiDoc'' at EDSIG Conference on Information Systems \& Computing Education\\

\years{} Outstanding officer award as Secretary of the Midwest Chapter of the Association for Information Systems

\section*{Publications \& Talks}

\textbf{*} Indicates student co-authors

\subsection*{Journal articles}
\noindent
\years{2021}Grimes, G. M., Schuetzler, R. M., \& Giboney, J.S. (2021). Mental Models and Expectation Violations in Conversational AI Interactions.
\emph{Decision Support Systems, 144}. \doi{https://doi.org/10.1016/j.dss.2021.113515}\\

\years{}Schuetzler, R. M., Grimes, G. M., Giboney, J. S., \& Rosser, H. K.\textbf{*} (2021). Deciding Whether and How to Deploy Chatbots.
\emph{MIS Quarterly Executive, 20}(1), p. 4.\\

\years{2020} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2020). 
The Impact of Chatbot Conversational Skill on Engagement and Perceived Humanness. 
\emph{Journal of Management Information Systems, 37}(3), pp.\ 875-900. 
\doi{https://doi.org/10.1080/07421222.2020.1790204}\\

\years{} Pickard, M., Schuetzler, R. M., Valacich, J. S., \& Wood, D. A. (2020). 
Innovative Accounting Interviewing: A Comparison of Real and Virtual Accounting Interviewers. 
\emph{The Accounting Review, 95}(6), pp.\ 339--366.
\doi{https://doi.org/10.2308/tar-2017-0235}\\

\years{} Young, J. A., Biros, D. P., Schuetzler, R. M., Smith, T. J., Stephens, P. R., 
Syler, R. A., \& Zheng, S. H. (2020) When Programs Collide: A Panel Report on the Competing 
Interests of Analytics and Security. \emph{Communications of the Association for Information Systems}, 
\emph{46}. \doi{https://doi.org/10.17705/1CAIS.04624}\\

\years{} Clarke, M. A., Schuetzler, R. M., Windle, J. R., Pachunka, E.\textbf{*}, \& Fruhling, F. (2020). 
Usability and Cognitive Load in the Design of a Personal Health Record. 
\emph{Health Policy and Technology, 9}(2), pp.\ 218--224. \doi{https://doi.org/10.1016/j.hlpt.2019.10.002}\\

\years{2019} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2019). 
The Effect of Conversational Agent Skill on User Behavior during Deception. 
\emph{Computers in Human Behavior, 97}, pp.\ 250--259. \doi{https://doi.org/10.1016/j.chb.2019.03.033}\\

\years{}Marquardson, J. \& Schuetzler, R. M. (2019). Teaching Tip: Learning by Teaching through Collaborative Tutorial Creation: Experience using GitHub and AsciiDoc. \emph{Journal of Information Systems Education, 30}(1), pp.\ 10--18.\\

\years{2018}Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Nunamaker, J. F. (2018).
The Influence of Conversational Agent Embodiment and Conversational Relevance on Socially Desirable Responding.
\emph{Decision Support Systems, 114}, pp.\ 94--102. \doi{https://doi.org/10.1016/j.dss.2018.08.011}\\

\years{2017} Payne, K., Keith, M. J., Schuetzler, R. M., \& Giboney, J. S. (2017)
Examining the Learning Effects of Live Streaming Video Game Instruction over
Twitch. \emph{Computers in Human Behavior, 77}, pp.\ 95--109. \doi{https://doi.org/10.1016/j.chb.2017.08.029}\\

\years{} Dunbar, N. E., Jensen, M. L., Miller, C. H., \ldots{}, \& Schuetzler,
R. M. (2017) Mitigation of Cognitive Bias with a Serious Game: Two Experiments
Testing Feedback Timing and Source, \emph{International Journal of Game-based
	Learning, 7}(4), pp.\ 86--100. \doi{https://doi.org/10.4018/IJGBL.2017100105}\\

\years{2016} Proudfoot, J. G., Boyle, R., \& Schuetzler, R. M. (2016) Man
vs. machine: Investigating the effects of adversarial system use on end-user
behavior in automated deception detection interviews. \emph{Decision Support
	Systems, 85}, pp.\ 23--33. \doi{https://doi.org/10.1016/j.dss.2016.02.008}\\

\years{2015} Twyman, N. T., Proudfoot, J. G., Schuetzler, R., Elkins,
A. C., \& Derrick, D. C. (2015). Robustness of multiple indicators in
controlled, automated deception detection interviews. \emph{Journal of
	Management Information Systems, 32}(4), pp.\ 215--245. \doi{https://doi.org/10.1080/07421222.2015.1138569}\\

\years{}Lowry, P. B., Schuetzler, R. M., Giboney, J. S., \& Gregory, T. (2015) Is
trust always better than distrust? The potential value of distrust in newer virtual teams
engaged in short-term decision making. \emph{Group Decision and
	Negotiation}, \emph{24}(4), pp.\ 723--753. \doi{http://dx.doi.org/10.1007/s10726-014-9410-x}\\

\years{}Burgoon, J. K., Schuetzler, R., \& Wilson, D. W. (2015) Kinesic patterning in
deceptive and truthful interactions.  \emph{Journal of Nonverbal Behavior}, \emph{39}(1), pp.\ 1--24. \doi{http://dx.doi.org/10.1007/s10919-014-0190-4}\\


\years{2014}Burgoon, J. K., Proudfoot, J. G., Schuetzler, R., \& Wilson, D. W. (2014)
Patterns of nonverbal behavior associated with truth and deception: Illustrations from
three experiments. \emph{Journal of Nonverbal
	Behavior}, \emph{38}(3), pp.\ 325--354. \doi{http://dx.doi.org/10.1007/s10919-014-0181-5}\\

\years{2011}Barlow, J. B., Giboney, J. S., Keith, M. J., Wilson, D. W., Schuetzler, R.,
Lowry, P. B., \& Vance, A. (2011). Overview and guidance on agile development in large
organizations. \emph{Communications of the Association for Information Systems}, \emph{29},
pp.\ 25--44. \doi{https://doi.org/10.17705/1CAIS.02902}

\newpage

\subsection*{Book chapters}
\noindent

\years{2016}Burgoon, J. K., Wilson, D., Hass, M., \& Schuetzler, R. (2016). Interactive Deception in Group Decision-Making: New Insights from Communication Pattern Analysis. In S. M. Magnusson, K. J. Burgoon, \& M. Casarrubea (Eds.), Discovering Hidden Temporal Patterns in Behavior and Interaction: T-Pattern Detection and Analysis with THEME™ (pp. 37–62). New York, NY: Springer New York. Retrieved from \doi{http://dx.doi.org/10.1007/978-1-4939-3249-8_2}

\subsection*{Conference proceedings}
\noindent
\years{2022}Schuetzler, R., Giboney, J., \& Grimes, G. M. (2022). Design of a Chatbot Social Engineering Victim. \emph{Hawaii International Conference on System Sciences}. January 3--7.\\

\years{}Leavitt, C.\textbf{*}, Corbin, M.\textbf{*}, Keith, M., Schuetzler, R., Anderson, G., \& Kettles, D. (2022). A Chatbot Tutor Can Lessen the Gender Confidence Gap in Information Systems Learning. \emph{Hawaii International Conference on System Sciences}. January 3--7.\\

\years{2021}Giboney, J. S., Schuetzler, R., Grimes, G. M., \& Dayley, I.\textbf{*} (2021). A Social Engineering Victim Chatbot to Teach Adversarial Thinking. \emph{Americas Conference on Information Systems}, Montreal, Qu\'ebec, Canada, August 9--13.\\

\years{}Corbin, M., Leavitt, C., Keith, M., Schuetzler, R., Kettles, D. J., \& Anderson, G. (2021). The Efficacy of Help Seeking on Creative Self-Efficacy of IS Students. \emph{Americas Conference on Information Systems}, Montreal, Qu\'ebec, Canada, August 9--13.\\

\years{2019}Pachunka, E., Windle, J., Schuetzler, R., \& Fruhling, A. (2019). Natural-Setting PHR Usability Evaluation using the NASA TLX to Measure Cognitive Load of Patients. \emph{Hawaii International Conference on System Sciences}. Grand Wailea, Maui, HI, January 8--11. \doi{https://doi.org/10.24251/HICSS.2019.480}\\

\years{}Schuetzler, R. M., Morrison, B. B., \& Hayes, J. (2019). Digital Excellence: A Missing Link. \emph{Americas Conference on Information Systems}, Canc\'{u}n, Mexico, August 15--17.\\

\years{}Schuetzler, R. M., Clarke, M. A., Windle, J. R., Pachunka, E., \& Fruhling, A. L. (2019). Understanding System-induced Cognitive Load with Eye Tracking. \emph{Americas Conference on Information Systems}, Canc\'{u}n, Mexico, August 15--17.\\

\years{2018}Pickard, M. D., Schuetzler, R. M., Valacich, J. S., \& Wood, D. (2018).
Next-Generation Accounting Interviewing: A Comparison of Human and Embodied Conversational Agents (ECAs) as Interviewers.
\emph{American Accounting Association Midyear Meeting}, Newport Beach, CA, January 18--20.\\

\years{} Marquardson, J. \& Schuetzler, R. M. (2018).
Learning by Teaching through Collaborative Tutorial Creation: Experience using GitHub and AsciiDoc.
\emph{EDSIG Conference on Information Systems \& Computing Education}, Norfolk, VA, October 31--November 3.\\

\years{} Schuetzler, R. M., Grimes, G. M., \& Giboney, J. S. (2018).
An Investigation of Conversational Agent Relevance, Presence, and Engagement
\emph{Americas Conference on Information Systems}, New Orleans, LA, August 15--18.\\

\years{} Fruhling, A. L., Ramachandran, D., Bernard, T., Schuetzler, R. M., \& Windle, J. (2018)
Patient Preferences for Authentication and Security: A Comparison Study of Younger and Older Patients.
\emph{ACM SIGMIS Conference on Computers and People Research}, Buffalo, NY, June 18--20. \doi{https://doi.org/10.1145/3209626.3209702}\\

\years{} Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Nunamaker, J.
F. (2018) The Influence of Conversational Agents on Socially Desirable
Responding. \emph{Hawaii International Conference on System Sciences}. Waikoloa Village, HI, January 3--6. \doi{https://doi.org/10.24251/HICSS.2018.038}\\

\years{2016} Schuetzler, R. M., Grimes, G. M., Elkins, A. C., Burgoon, J. K., \&
Valacich, J. S. (2016) Talking and typing: A comparison of vocalic and keystroke
dynamic features for deception detection. \emph{Hawaii International Conference
	on System Sciences}. Koloa, HI, January 5--8.\\

\years{2015}Wilson, D. W., Schuetzler, R. M., Dorn, B., Proudfoot, J. G., \&
Valacich, J. S. (2015) When disclosure is involuntary: Empowering users with
control to reduce concerns. \emph{International Conference on Information
	Systems}. Fort Worth, Texas, December 13--16.\\

\years{2014}Schuetzler, R. M., Giboney, J. S., Grimes, G. M., \& Buckman,
J. (2014) Facilitating natural conversational agent interactions: Lessons from a
deception experiment. \emph{International Conference on Information Systems}. Auckland, New Zealand, December 12-16.\\

Dunbar, N. E., Jensen, M. L., Miller, C. H., Bessarabova, E.,
Straub, S., \ldots~\& Schuetzler, R. (2014) Mitigating cognitive bias through
the use of serious games: Effects of feedback. \emph{9th International
	Conference on
	Persuasive Technology}, Padova, Italy, May 21-23. \doi{https://doi.org/10.1007/978-3-319-07127-5_9}\\

\years{2013}Twyman, N. W., Schuetzler, R., Proudfoot, J. G., \& Elkins,
A. (2013). A systems approach to countermeasures in credibility assessment
interviews. \emph{International Conference on Information Systems (ICIS)},
Milan, Italy, December 15--18.\\

Schuetzler, R. \& Wilson, D. W. (2013) Real-time embodied agent
adaptation. \emph{Hawaii International Conference on System Sciences}.\\


\years{2012}Schuetzler, R. (2012) Countermeasures and eye tracking deception
detection. \emph{Hawaii International Conference on System Sciences}.\\

Nunamaker, J. F., Jr., Burgoon, J. K., Twyman, N. W., Proudfoot, J. G.,
Schuetzler, R., \& Giboney, J. S. (2012) Establishing a foundation for human
credibility screening. \emph{2012 IEEE International Conference on Intelligence	and Security Informatics (ISI)}. June 11--14.\\

Burgoon, J. K., Wilson, D. W., Schuetzler, R. \& Hass, M. (2012) Interactive
deception in group decision-making. \emph{National Communication Association
	Convention}.\\

Burgoon, J. K., Schuetzler, R., \& Wilson, D. W. (2012) Uncovering hidden
patterning in interpersonal communication: Illustration with deceptive and
truthful interactions. \emph{National Communication Association Convention}.\\

\years{2011}Proudfoot, J. G., Giboney, J. S., Schuetzler, R. \& Durcikova,
A. (2011). Trends in phishing attacks: Suggestions for future
research. \emph{Americas Conference on Information Systems}.\\

\years{2010}Lowry, P. B., Giboney, J. S., Schuetzler, R., Richardson, J.,
Gregory, T., Romney, J., \& Anderson, B. (2010). The value of distrust in
computer-based decision-making groups. In \emph{Proceedings of the 43rd Hawaii
International Conference on System Sciences}.


\subsection*{Invited Presentations and Panels}
\noindent
\years{2021}\emph{The Value of Tailoring and Small Talk}. Presentation at the Dagstuhl Seminar: Conversational Agent as Trustworthy Autonomous System (Trust-CA).\\

\years{2019}\emph{When Programs Collide: Competing Interests of Analytics and Security}. Panel at the annual conference of the Midwest Chapter of the AIS. Panel report published in \emph{Communications of the Association for Information Systems}.\\

\years{}\emph{Extending Engagement with Discussion Boards}. Presentation at the UNO STEM TRAIL Center Pedagogy Workshop.\\

\years{}\emph{Fostering a Community of Inquiry with Discourse(.org)}. Presentation at the 2nd annual UNO Digital Learning Showcase.\\

\years{2018}\emph{Developing Instructor Presence Online}. Presentation at the 1st annual UNO Digital Learning Showcase.\\

\years{}\emph{Extending the Conversation about Teaching with Technology}. Panel at the University of Nebraska Technology and Pedagogy Symposium.\\

\years{2016}\emph{Chatbot for Enhancing Voluntary Information Disclosure}. Webinar for the Center for Identification
Technology Research, an NSF Industry/University Collaborative Research Center.\\

\years{2015}\emph{Lie to Me: Chatterbot Style}. Webinar for the Center for Identification
Technology Research, an NSF Industry/University Collaborative Research Center.\\

\years{2014}\emph{Identifying and Reducing Patient Drug Seeking}. Panel for first-year
medical students at University of Arizona College of Medicine.\\

\emph{A Mobile Interviewing Agent for Deception Detection}. Webinar for the
Center for Identification Technology Research, an NSF Industry/University Collaborative
Research Center.\\

\years{2012-2014}\emph{Deception and Automated Credibility Assessment}. Fort Huachuca
Military Intelligence Captain's Career course.


\section*{Teaching}

\subsection*{Teaching Narrative}

The primary courses I have taught are data communications/IT infrastructure
and computer security management. I have successfully adapted both courses for 
online learning, and continue to teach in both modes. My courses involve a variety of activities,
including open access hands-on lab activities I have created to allow students to 
see the concepts they learn about in action. 
% My teaching is centered around one principle: I want students to love the
% material I teach in the class. I start each semester telling my students just
% that. I tell them that if they don't love them, I want them to at least like
% it; and if not like it, then at least understand it. In order to foster that
% attitude, I believe in creating an interactive classroom where I am not the only
% one instructing. I design my class in a way to allow students to contribute and
% teach each other. I also fully admit to my students that I do not know
% everything, and show my own love of the material by seeking answers to student
% questions that stump me during class.\\

% My in-class activities are centered around ensuring that students learn,
% understand, and apply their knowledge. Regular hands-on activities and in-class
% small group activities help students solidify their knowledge in a way that my
% lecturing cannot. In any way possible, I strive to give students the basic
% knowledge that they need in order to teach themselves. There is not enough time
% in a semester, or in an entire university education, to learn everything one
% must know in this world of ever-advancing technology. So I see my role as giving
% students the basic pieces that they can later put together in new and exciting
% ways.

% I believe that the purpose of a university education is to teach students how to
% think and how to learn. With the ever-changing technological landscape, the need
% to memorize information is nearly nonexistent. As such, my instruction focuses
% on giving students the hands-on experience and skills that they could not easily
% Google in the future. I believe in equipping students with a level of knowledge
% and understanding of course topics so they can converse intelligently and
% understand reference material easily available on the web.\\

% My course instruction centers on class participation and understanding. When
% possible I bring hands-on lab exercises and learning activities to aid students
% in internalizing course material.

\subsection*{Courses Taught}
\subsubsection*{Brigham Young University}

\years{2021--present}IS 404 -- Data Communications (Overall rating: 4.8/5.0)\\

\subsubsection*{University of Nebraska at Omaha}

\years{2017--2020}CYBR/ISQA 8546 -- Computer Security Management (Overall rating: 4.42/5.0)\\

\years{2015--2020}ISQA 3400 -- Business Data Communications (Overall rating: 4.55/5.0)\\

\years{2016--2020}ISQA 8310 -- Data Communications (Overall rating: 4.65/5.0)\\

\years{2016--2019}ISQA 4380 -- Distributed Systems and Technologies (Overall rating: 4.48/5.0)\\


\subsubsection*{University of Arizona}
\years{2013-2015}MIS 307 -- Introduction to Business Data Communications (Effectiveness: 4.6/5.0)\\

\years{2012}MIS 111 -- Introduction to Management Information Systems
(Effectiveness: 4.9/5.0)

\subsection*{Course Achievements}
\begin{itemize}
	\itemsep0em
	\item Transitioned IT Infrastructure, Computer Security Management, and Distributed Technologies classes to online learning
	\item Fully updated former data communications course to IT Infrastructure, including new content introducing operating systems and cloud computing.
	\item Created virtual labs for IT Infrastructure to allow students to gain hands-on experience with data communications (Creative Commons licensed, and available on \href{https://github.com/rschuetzler/datacom-labs}{GitHub})
	\item Created a discussion board using the open source Discourse program to provide a more flexible and dynamic conversation platform for student-student interactions
	\item Converted IT Infrastructure course to use Open Educational Resources (OER) to improve flexibility and reduce costs for students
	\item Online course featured in the 2020 UNO Chancellor's strategic planning forum
\end{itemize}


\subsection*{Select Student Comments}

\begin{quote}
	I appreciated your passion and it encouraged me to work harder and study better for this
	course\ldots I fully digested the information you presented to us. After completing this
	course, I am seriously considering spending more time in the areas you taught us because
	I have found a curiosity for the area I did not imagine before.
\end{quote}

\begin{quote}
	I really enjoy class. The way the material has been amplified with your own knowledge
	and the way the slides are structured really help me to pay attention, take notes, and
	tell myself "Ooo, that's something I want to put down here. That's important."
\end{quote}

\begin{quote}
	Great teacher, made everything very easy to understand. Made class interesting and
	fun. Kept everyone engaged in learning.
\end{quote}

\begin{quote}
	I really enjoyed that Ryan truly cared if his students understood what was going on and
	comprehended the material.
\end{quote}

%\hrule
\section*{Service}

\subsection*{Conference and AIS Activities}

\begin{itemize}
	\itemsep0em
	\item Mini-track Associate Editor (ICIS 2021): Human-Robot Interaction
	\item Mini-track chair (AMCIS 2018--present): Cognitive, Affective, and Conversational HCI
	\item Mini-track co-chair (HICSS 2019--2022): Design and Development of Collaboration Technologies
	\item President of the Midwest chapter of the Association for Information Systems (2019--2020)
	\item Secretary for Midwest chapter of the Association for Information Systems (2016--2018)
	\item Conference chair: Big XII+ Management Information Systems Symposium (2017, Omaha)
\end{itemize}

\subsection*{Reviewing}

\subsubsection*{Grants}
\begin{itemize}
	\itemsep0em
	\item Dutch Research Council (2020)
\end{itemize}

\subsubsection*{Journals}

\begin{itemize}
	\itemsep0em
	\item International Journal for Human-Computer Interaction
	\item MIS Quarterly
	\item Journal of Management Information Systems
	\item Journal of the Association for Information Systems
	\item Computers in Human Behavior
	\item Decision Support Systems
	\item Journal of the Midwest Association for Information Systems
	\item ACM Transactions on Management Information Systems
	\item Group Decision \& Negotiation
	\item Journal of Nonverbal Behavior
	\item IEEE, SMC-A
\end{itemize}

\subsubsection*{Conferences}

\begin{itemize}
	\itemsep0em
	\item EDSIG Conference on Information Systems \& Computing Education
	\item International Conference on Information Systems
	\item Hawaii International Conference on System Sciences
	\item Americas Conference on Information Systems
	\item European Conference on Information Systems
	\item AIS Special Interest Group on Human-Computer Interaction (SIGHCI)
\end{itemize}

\subsection*{Department/University}

\begin{itemize}
	\itemsep0em
	\item ISQA Department Undergraduate Program Committee Chair (2017--2020)
	\item IS\&T Doctoral Program Committee Member (2019--present)
	\item IS\&T Faculty Liaison for Instructional Design (2017--2019)
	\item IS\&T Advisory Committee Member (2018--2019)
	\item Biomedical Informatics Doctoral Program Committee Member (2018--2019)
	\item ISQA Department Undergraduate Program Committee Member (2016--2017)
	\item UNO Success Academy Faculty Presenter (2016--2017)
\end{itemize}

\subsection*{Community}
\begin{itemize}
	\itemsep0em
	\item Omaha Python User Group: Arranged campus hosting for monthly meetings and presented on conversational agent research (2018)
\end{itemize}


% \section*{Consulting Clients}
% \begin{itemize}
% \itemsep0em
% \item Wal-Mart (Bentonville, AR)
% \begin{itemize}
%   \itemsep0em
%   \item 2010: Research and strategic development for agile software development
%     within Wal-Mart's current SDLC
% \end{itemize}
% \end{itemize}

\section*{Technical and Other Skills}

\begin{itemize}
	\itemsep0em
	\item Programming languages: Python, R, Node.js
	\item AWS
	\item Web application development with Python and Django
	\item TCP/IP networking (previously CCNA certified)
	\item SQL \& database management
	\item Linux and Windows servers
	\item Spanish: Moderate proficiency
\end{itemize}


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
	{\scriptsize  Last updated: \today\- •\-
		% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
		Typeset in \href{http://nitens.org/taraborelli/cvtex}{
			%\fontspec{Times New Roman}
			\XeTeX }\\
		% ---- FILL IN THE FULL URL TO YOUR CV HERE
		% \href{http://nitens.org/taraborelli/cvtex}{http://nitens.org/taraborelli/cvtex}
	}
\end{center}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
